DisCon Adult Study 2

### 2018-09-12 analysis/01_kids_summary.Rmd
datasets

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
         subage = ifelse(subid == '180831_5', 2, subage)) # child 180831_5 is 2 but recorded as 3
```

>>>>

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
         subage = ifelse(subid == '180831_5', 2, subage)) # child 180831_5 is 2 but recorded as 3

write.csv(data, file="../data/01_kids_summary.data.csv")

data <- read_csv(file="../data/pilot.data.csv")
```

### 2018-09-12 analysis/01_pilot_summary.Rmd
datasets

@@

#Combine recency data
data_recency <- bind_rows(data_recency_another, data_recency_last, data_recency_look)
```

>>>>

write.csv(data_pilot_another, file="../data/01_piot_summary_pilot_another.data.csv")
data_pilot_another <- read_csv(file="../data/01_piot_summary_pilot_another.data.csv")

@@

#Combine recency data
data_recency <- bind_rows(data_recency_another, data_recency_last, data_recency_look)

write.csv(data_recency, file="../data/01_piot_summary_recency.data.csv")
data_recency <- read_csv(file="../data/01_piot_summary_recency.data.csv")
```

### 2018-09-12 analysis/01_study1_adult.Rmd
analysis files for adults and kids
datasets

@@

data_low <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
```

@@

>>>>

write.csv(data_high, file="../data/01_study1_adult_high.data.csv")
data_high <- read_csv(file="../data/01_study1_adult_high.data.csv")

@@

data_low <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))

write.csv(data_high, file="../data/01_study1_adult_low.data.csv")
data_low <- read_csv(file="../data/01_study1_adult_low.data.csv")

```

@@

saveRDS(bm1, "01_study1_adult_models/bm1.rds")
saveRDS(bm2, "01_study1_adult_models/bm2.rds")

### 2018-09-12 analysis/01_study2_adult.Rmd
datasets

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
```

>>>>

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))

write.csv(data, file="../data/01_study2_adult.data.csv")
data <- read_csv(file="../data/01_study2_adult.data.csv")
```
